Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-17 manuscript/manuscript.Rmd
fixes references

Estimating parameter variability in space and time is critical when using population models to forecast responses to directional changes in exogoneous drivers like climate [@Clark2011; @Vanderwel2013; @Wolkovich2014a; @Petchey2015]. Compared to demographic models, density-structured modeling approaches may provide an efficient route toward estimating such uncertainty. However, population models based on aggregated inidividual data have yet to be tested with climate drivers. Since it is individuals that respond to weather, rather than populations, models based on a aggregated data may produce incorrect forecasts [@Clark2012]. Thus, we sought to compare climate sensitivities of individual and population based models of four grassland species populations.

>>>>

Estimating parameter variability in space and time is critical when using population models to forecast responses to directional changes in exogoneous drivers like climate [@Clark2011; @Vanderwel2013; @Wolkovich2014; @Petchey2015]. Compared to demographic models, density-structured modeling approaches may provide an efficient route toward estimating such uncertainty. However, population models based on aggregated inidividual data have yet to be tested with climate drivers. Since it is individuals that respond to weather, rather than populations, models based on a aggregated data may produce incorrect forecasts [@Clark2012]. Thus, we sought to compare climate sensitivities of individual and population based models of four grassland species populations.

### 2015-06-17 manuscript/manuscript.tex
fixes references

Equilibrium cover from both models was sensitive to climate (Fig. 2a-d).
The IPM projected percent changes in equilibrium cover from -3 - 8\% for
\emph{B. gracilis}, -4 - 3\% for \emph{H. comata}, -15 - 9\% for
\emph{P. smithii}, and -17 - 53\% for \emph{P. secunda}. The QBM
projected opposite and greater percent changes in equilibrium cover for
\emph{B. gracilis} (-63 - 30\%) and \emph{H. comata} (-50 - -18\%; Fig.
2a-b). For \emph{P. smithii}, the QBM projected opposite changes in
equilibrium cover than the IPM, but of similar magnitude (-5 - 6\%; Fig.
2C). \emph{P. secunda} was the only species that the IPM and QBM made
projections of the same sign and somewhat similar magnitude (Fig. 2d).
As expected based on model validation (Table 1), IPM projections were
more uncertain than QBM projections for all species and all climate
change scenarios (Fig. 2e-h).

@@

Estimating parameter variability in space and time is critical when
using population models to forecast responses to directional changes in
exogoneous drivers like climate ({\textbf{???}}, {\textbf{???}},
{\textbf{???}}, {\textbf{???}}). Compared to demographic models,
density-structured modeling approaches may provide an efficient route
toward estimating such uncertainty. However, population models based on
aggregated inidividual data have yet to be tested with climate drivers.
Since it is individuals that respond to weather, rather than
populations, models based on a aggregated data may produce incorrect
forecasts (Clark et al. 2012). Thus, we sought to compare climate
sensitivities of individual and population based models of four
grassland species populations.

@@

>>>>

Equilibrium cover from both models was sensitive to climate (Fig. 2a-d).
The IPM projected percent changes in equilibrium cover from -3 - 8\% for
\emph{B. gracilis}, -4 - 3\% for \emph{H. comata}, -15 - 9\% for
\emph{P. smithii}, and -17 - 53\% for \emph{P. secunda}. The QBM
projected opposite and greater percent changes in equilibrium cover for
\emph{B. gracilis} (-63 - 30\%) and \emph{H. comata} (-50 - -18\%; Fig.
2a-b). For \emph{P. smithii}, the QBM projected opposite changes in
equilibrium cover than the IPM, but of similar magnitude (-5 - 6\%; Fig.
2c). \emph{P. secunda} was the only species that the IPM and QBM made
projections of the same sign and somewhat similar magnitude (Fig. 2d).
As expected based on model validation (Table 1), IPM projections were
more uncertain than QBM projections for all species and all climate
change scenarios (Fig. 2e-h).

@@

Estimating parameter variability in space and time is critical when
using population models to forecast responses to directional changes in
exogoneous drivers like climate (Clark et al. 2011, Vanderwel et al.
2013, Wolkovich et al. 2014, Petchey et al. 2015). Compared to
demographic models, density-structured modeling approaches may provide
an efficient route toward estimating such uncertainty. However,
population models based on aggregated inidividual data have yet to be
tested with climate drivers. Since it is individuals that respond to
weather, rather than populations, models based on a aggregated data may
produce incorrect forecasts (Clark et al. 2012). Thus, we sought to
compare climate sensitivities of individual and population based models
of four grassland species populations.

@@

Petchey, O. L., M. Pontarp, T. M. Massie, S. Kéfi, A. Ozgul, M.
Weilenmann, G. M. Palamara, F. Altermatt, B. Matthews, J. M. Levine, D.
Z. Childs, B. J. McGill, M. E. Schaepman, B. Schmid, P. Spaak, A. P.
Beckerman, F. Pennekamp, and I. S. Pearse. 2015. The ecological forecast
horizon, and examples of its uses and determinants. Ecology Letters
18:597--611.
